Figures and supplemental figures for ecological resilience ms

### 2023-12-24 ms_figures_supp_figs.qmd
Clean docs (#1)
* refactor all code for main figs to streamline and/or use functions

* clean up supp figure plots

* finish refactor of ms_figures_supp_figs.qmd

# # use species specific vB params to create a weight at age data.frame that can be used to convert abundance at age to biomass at age
# species_name <- brf_mei_lp_nice[[2]]
# brf_waa_g <- sim_species_parms[[species_name]][["biom_const"]] * sim_species_derived_vars[[species_name]][["length_at_age"]] ^
#                     sim_species_parms[[species_name]][["biom_exp"]]
# 
# brf_waa_g_df <- data.frame(age = 1: sim_species_parms[[species_name]]$A_max,
#                            waa_g = brf_waa_g)
# 
# # use functions to create useful data structures
# # FLEP to F reference tables by species
# spec_fleps_2_fs <-
#   get_fs_from_fleps(species = species_name,
#                     flep_inds = species_flep_fished_ind,
#                     f_vals =  fishing_mortality_values)

@@

# Species: Blue rockfish
# Dispersal: No Dispersal
# Environmental noise: White

p1 <-
  plot_contour_bm_below_thresh(sum_stats_f_frac_df = ,
                               spec_disp_noise = )

p2 <-
  plot_contour_yld_below_thresh(sum_stats_f_frac_df = ,
                                spec_disp_noise = )

con <- DBI::dbConnect(duckdb::duckdb(),
                        dbdir = "data/sim_out.duckdb",
                        read_only = FALSE)

# use functions to create useful data structures
# FLEP to F reference tables by species
spec_fleps_2_fs <-
  get_fs_from_fleps(species = species_name,
                    flep_inds = species_flep_fished_ind,
                    f_vals =  fishing_mortality_values)

## Qry 
qry <- paste0("SELECT  sim_num, reserve_frac, flep_ratio, year, age, 
              sum(number) as abundance,
              sum(yield) as yield,
              FROM '", table_name_nd_white, 
              "' WHERE sim_num IN (", toString(sims_2_use), ") AND year > 500 
              GROUP BY sim_num, reserve_frac, flep_ratio, year, age
              ORDER BY sim_num, reserve_frac, flep_ratio, year, age
              ")

sim_res_out <- dbGetQuery(conn = con, qry)

F_brf_maxes_yield <- get_f_maxes_yield(input_df = sim_res_out,
                                         fleps_2_fs = spec_fleps_2_fs)
F_brf_maxes_yield

out_fs <- df_add_fs_out (input_df = sim_res_out,
                         spec_fleps_2_fs = spec_fleps_2_fs,
                         F_maxes_yield = F_brf_maxes_yield, waa_g_df = brf_waa_g_df)
out_fs

med_yield <- get_median_yield(input_df = out_fs) 
med_yield

med_biomass <- get_median_biomass(input_df = out_fs, age_mat = sim_species_parms$`Blue rockfish`$A_mat)
med_biomass

out_yld_bm_sims_f_frac_yr <-
  df_yld_bm_stats_by_sim_f_frac_year(input_df = out_fs,
                                     age_mat = sim_species_parms$`Blue rockfish`$A_mat)#, sims_num_2_use = sims_2_use

# out_yld_bm_sims_f_frac_yr
# pipeline works to here

sum_stats_f_frac_df <-
  summary_stats_by_f_frac(
    out_sim_f_frac_yr = out_yld_bm_sims_f_frac_yr,
    median_yield = med_yield,
    median_biomass = med_biomass
  )
sum_stats_f_frac_df

p1 <- sum_stats_f_frac_df[[2]] %>%
  filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
  ggplot(.,
       aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_biomass_thresh)) +
  metR::geom_contour_fill(bins = 12) +
  ggtitle(paste0(
        brf_white_nd_nice[[2]],
        " ",
        brf_white_nd_nice[[1]],
        " ",
        brf_white_nd_nice[[3]],
        ":\nTime below mean median biomass "
      )) +
      xlab("Fraction of coastline in reserves") +
      ylab("Harvest Rate (F/Fmsy)") +
      scale_fill_viridis_c(option = "D", direction = -1) +
      geom_segment(aes(
        x = 0,
        xend = max_reserve_frac,
        y = 1,
        yend = 1
      ), colour = "black",
      linetype = 2) +
      scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
      scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
      theme_bw()

p2 <- sum_stats_f_frac_df[[2]] %>%
  filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
  ggplot(.,
       aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_yield_thresh)) +
  metR::geom_contour_fill(bins = 12) + 
  ggtitle(paste0(
        brf_white_nd_nice[[2]],
        " ",
        brf_white_nd_nice[[1]],
        " ",
        brf_white_nd_nice[[3]],
        ":\nTime below median max yield"
      )) +
      xlab("Fraction of coastline in reserves") +
      ylab("Harvest Rate (F/Fmsy)") +
      scale_fill_viridis_c(option = "D", direction = -1) +
      geom_segment(aes(
        x = 0,
        xend = max_reserve_frac,
        y = 1,
        yend = 1
      ), colour = "black",
      linetype = 2) +
      scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
      scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
      theme_bw()

# Species: Blue rockfish
# Dispersal: Larval Pool Dispersal
# Environmental noise: White
# use species specific vB params to create a weight at age data.frame that can be used to convert abundance at age to biomass at age
species_name <- brf_mei_lp_nice[[2]]
brf_waa_g <- sim_species_parms[[species_name]][["biom_const"]] * sim_species_derived_vars[[species_name]][["length_at_age"]] ^
                    sim_species_parms[[species_name]][["biom_exp"]]

# use functions to create useful data structures
# FLEP to F reference tables by species
spec_fleps_2_fs <-
  get_fs_from_fleps(species = species_name,
                    flep_inds = species_flep_fished_ind,
                    f_vals =  fishing_mortality_values)

## Qry 
qry <- paste0("SELECT  sim_num, reserve_frac, flep_ratio, year, age, 
              sum(number) as abundance,
              sum(yield) as yield,
              FROM '", table_name_lp_white, 
              "' WHERE sim_num IN (", toString(sims_2_use), ") AND year > 500 
              GROUP BY sim_num, reserve_frac, flep_ratio, year, age
              ORDER BY sim_num, reserve_frac, flep_ratio, year, age
              ")

sim_res_out <- dbGetQuery(conn = con, qry)

#######

########### PIPELINING
F_brf_maxes_yield <- get_f_maxes_yield(input_df = sim_res_out,
                                         fleps_2_fs = spec_fleps_2_fs)
F_brf_maxes_yield

out_fs <- df_add_fs_out (input_df = sim_res_out,
                         spec_fleps_2_fs = spec_fleps_2_fs,
                         F_maxes_yield = F_brf_maxes_yield, waa_g_df = brf_waa_g_df)
out_fs

med_yield <- get_median_yield(input_df = out_fs) 
med_yield

med_biomass <- get_median_biomass(input_df = out_fs,
                                  age_mat = sim_species_parms$`Blue rockfish`$A_mat)
med_biomass

out_yld_bm_sims_f_frac_yr <-
  df_yld_bm_stats_by_sim_f_frac_year(input_df = out_fs, 
                                     age_mat = sim_species_parms$`Blue rockfish`$A_mat)

# pipeline works to here

sum_stats_f_frac_df <-
  summary_stats_by_f_frac(
    out_sim_f_frac_yr = out_yld_bm_sims_f_frac_yr,
    median_yield = med_yield,
    median_biomass = med_biomass
  )
sum_stats_f_frac_df

p3 <- sum_stats_f_frac_df[[2]] %>%
  filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
  ggplot(.,
       aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_biomass_thresh)) +
  metR::geom_contour_fill(bins = 12) +
  ggtitle(paste0(
        brf_white_lp_nice[[2]],
        " ",
        brf_white_lp_nice[[1]],
        " ",
        brf_white_lp_nice[[3]],
        ":\nTime below mean median biomass "
      )) +
      xlab("Fraction of coastline in reserves") +
      ylab("Harvest Rate (F/Fmsy)") +
      scale_fill_viridis_c(option = "D", direction = -1) +
      geom_segment(aes(
        x = 0,
        xend = max_reserve_frac,
        y = 1,
        yend = 1
      ), colour = "black",
      linetype = 2) +
      scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
      scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
      theme_bw()

p4 <- sum_stats_f_frac_df[[2]] %>%
  filter(as.numeric(reserve_frac) <= max_reserve_frac, f_fmsy <= max_f_fmsy) %>%
  ggplot(.,
       aes(x = as.numeric(reserve_frac), y = f_fmsy, z = yrs_below_yield_thresh)) +
  metR::geom_contour_fill(bins = 12) + 
  ggtitle(paste0(
        brf_white_lp_nice[[2]],
        " ",
        brf_white_lp_nice[[1]],
        " ",
        brf_white_lp_nice[[3]],
        ":\nTime below median max yield"
      )) +
      xlab("Fraction of coastline in reserves") +
      ylab("Harvest Rate (F/Fmsy)") +
      scale_fill_viridis_c(option = "D", direction = -1) +
      geom_segment(aes(
        x = 0,
        xend = max_reserve_frac,
        y = 1,
        yend = 1
      ), colour = "black",
      linetype = 2) +
      scale_x_continuous(expand = expansion(mult = 0, add = 0), limits = c(0, 0.3)) +
      scale_y_continuous(expand = expansion(mult = 0, add = 0)) +
      theme_bw()

# print(p1)
# print(p2)
# print(p3)
# print(p4)

p_s1 <- plot_grid(p1, p2, p3, p4, labels = letters[1:4], label_size = 9, byrow = FALSE)

@@

DBI::dbDisconnect(conn = con, shutdown=TRUE)

@@

### Supp Fig 4

Yield contours for Cabezon and China rockfish

-   white noise (or do we want ENSO?) --- white vs ENSO

-   Larval pool dispersal

```{r}
#| label: supp_fig_4
#| 
```

>>>>

@@

# Species: Blue rockfish
# Dispersal: No Dispersal/Larval Pool
# Environmental noise: White

sim_res_out_brf_nd_white <-
  qry_get_sim_data_for_analysis(table_name = table_name_brf_nd_white)
sim_res_out_brf_lp_white <-
  qry_get_sim_data_for_analysis(table_name = table_name_brf_lp_white)

F_brf_maxes_yield_brf_nd_white <-
  get_f_maxes_yield(input_df = sim_res_out_brf_nd_white,
                    fleps_2_fs = spec_fleps_2_fs_brf)
F_brf_maxes_yield_brf_lp_white <-
  get_f_maxes_yield(input_df = sim_res_out_brf_lp_white,
                    fleps_2_fs = spec_fleps_2_fs_brf)

out_fs_brf_nd_white <- df_add_fs_out(
  input_df = sim_res_out_brf_nd_white,
  spec_fleps_2_fs = spec_fleps_2_fs_brf,
  F_maxes_yield = F_brf_maxes_yield_brf_nd_white,
  waa_g_df = brf_waa_g_df
)
out_fs_brf_lp_white <- df_add_fs_out(
  input_df = sim_res_out_brf_lp_white,
  spec_fleps_2_fs = spec_fleps_2_fs_brf,
  F_maxes_yield = F_brf_maxes_yield_brf_lp_white,
  waa_g_df = brf_waa_g_df
)

med_yield_brf <- get_median_yield(input_df = out_fs_brf_nd_white)

med_biomass_brf <- get_median_biomass(input_df = out_fs_brf_nd_white)

out_yld_bm_sims_f_frac_yr_brf_nd_white <-
  df_yld_bm_stats_by_sim_f_frac_year(input_df = out_fs_brf_nd_white)
out_yld_bm_sims_f_frac_yr_brf_lp_white <-
  df_yld_bm_stats_by_sim_f_frac_year(input_df = out_fs_brf_lp_white)

sum_stats_f_frac_df_brf_nd_white <-
  summary_stats_by_f_frac(
    out_sim_f_frac_yr = out_yld_bm_sims_f_frac_yr_brf_nd_white,
    median_yield = med_yield_brf,
    median_biomass = med_biomass_brf
  )
sum_stats_f_frac_df_brf_lp_white <-
  summary_stats_by_f_frac(
    out_sim_f_frac_yr = out_yld_bm_sims_f_frac_yr_brf_lp_white,
    median_yield = med_yield_brf,
    median_biomass = med_biomass_brf
  )

## Plotting
p1 <-
  plot_contour_bm_below_thresh(sum_stats_f_frac_df = sum_stats_f_frac_df_brf_nd_white,
                               spec_disp_noise = brf_nd_white_nice)

p2 <-
  plot_contour_yld_below_thresh(sum_stats_f_frac_df = sum_stats_f_frac_df_brf_nd_white,
                                spec_disp_noise = brf_nd_white_nice)
p3 <-
  plot_contour_bm_below_thresh(sum_stats_f_frac_df = sum_stats_f_frac_df_brf_lp_white,
                               spec_disp_noise = brf_lp_white_nice)

p4 <-
  plot_contour_yld_below_thresh(sum_stats_f_frac_df = sum_stats_f_frac_df_brf_lp_white,
                                spec_disp_noise = brf_lp_white_nice)
p_s1 <-
  plot_grid(
    p1,
    p2,
    p3,
    p4,
    labels = letters[1:4],
    label_size = 9,
    byrow = FALSE
  )

@@

# DBI::dbDisconnect(conn = con, shutdown=TRUE)

@@

###
